The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-26 paper/sections/methods.tex
methods draft done, paper draft done :)

\section{Shape Matching Element Method}
 Each input object is composed of a set of boundary representations, $\Prts$, one for each part $\prt\in\Prts$. 
 Our kinematic mapping is a blended construction (as is done for skinning~\cite{10.1145/2614028.2615427}) which we write as

@@

We derive the mass matrix for our system from the definition of kinetic energy:
\begin{equation}
    T = \dot{\vc{q}}^T\underbrace{\Pi^T\int_{\Omega}\shapef\left(\refX\right)^Tshapef\left(\refX\right)d\Omega\Pi}_{\MM}\dot{\vc{q}},
\end{equation}
% \begin{equation}
% T = \frac{1}{2}\int_{ \Omega} \rho \dot{\mathbf{x}}^T\dot{\mathbf{x}} d\Omega
% \text{,}
% \end{equation}
% where $\Omega$ is the 3D integration domain, $\rho$ is the density, and $\dot{\mathbf{x}}$ is the velocity for some point in the domain. Using the deformation map defined in \ref{eqn:compact_x_map}, we may rewrite this kinetic energy as
% \begin{equation}
% \begin{split}
% T & = \frac{1}{2}\int_{ \Omega} \rho \dot{\mathbf{q}}^T \mathbf{J}^T\mathbf{Y(X)}^T\mathbf{Y(X)}\ d\Omega \\
%   & = \frac{1}{2} \dot{\mathbf{q}}^T \mathbf{J}^T \left[ \int_{ \Omega} \rho \mathbf{Y(X)}^T\mathbf{Y(X)} d\Omega \right] \mathbf{J}\dot{\mathbf{q}} \\
%   & = \frac{1}{2} \dot{\mathbf{q}}^T \mathbf{M} \dot{\mathbf{q}}
% \end{split}
% \text{.}
% \end{equation}
% The second line is a result of the fact that all terms except for $\mathbf{Y(X)}$ are spatially constant, allowing us to move these outside the volume integral, which enables fast assembly of the mass matrix, $\mathbf{M}$.

\subsection{Deformation Gradient}
% \dave{gotta deal with this weight gradient}
% At this point we have shown how to fit a polynomial describing the deformation of each surface. With these polynomial coefficients coupled with their associated centers of mass, we can construct an estimate of some arbitrary material point $\mathbf{X}$ using the deformation described by the surface. This lends itself to a general definition for the deformed position of a point as a weighted sum of the polynomials, which yields a unique polynomial for the point. Thus we arrive at a definition for the deformed position, $\mathbf{x}$, of a material point $\mathbf{X}$ in the undeformed space:
% \begin{equation}
% \label{eqn:deformation_map}
% 	\mathbf{x}(\mathbf{X}) = \sum_i^n w_i(\mathbf{X}) \left[ \mathbf{M}(\mathbf{X-\bar{X}}_j)\mathbf{c}_i + \mathbf{t}_j \right]
% 	\text{,}
% \end{equation}
% where we have $n$ surfaces, and $w_i$ and $\mathbf{c}_i$ are the weights and the coefficients for the $i$-th surface, respectively. The terms $\mathbf{\bar{X}}_j$ and $\mathbf{t}_j$ the undeformed and deformed centers of mass, respectively, that are associated with the $i$-th surface.

>>>>

\section{Shape Matching Element Method}
 Each input object is composed of a set of boundary representations, $\Prts$, one for each part $\prt\in\Prts$. 
 Our kinematic mapping is a blended construction~\cite{10.1145/2614028.2615427,blendedFORKS2016} which we write as

@@

We derive the mass matrix for our system from the definition of kinetic energy:
\begin{equation}
    T = \dot{\vc{q}}^T\underbrace{\Pi^T\int_{\Omega}\bldmat\left(\refX\right)^T\shapef\left(\refX\right)^T\shapef\left(\refX\right)\bldmat\left(\refX\right)d\Omega\Pi}_{\MM}\dot{\vc{q}},
\end{equation}
% \begin{equation}
% T = \frac{1}{2}\int_{ \Omega} \rho \dot{\mathbf{x}}^T\dot{\mathbf{x}} d\Omega
% \text{,}
% \end{equation}
% where $\Omega$ is the 3D integration domain, $\rho$ is the density, and $\dot{\mathbf{x}}$ is the velocity for some point in the domain. Using the deformation map defined in \ref{eqn:compact_x_map}, we may rewrite this kinetic energy as
% \begin{equation}
% \begin{split}
% T & = \frac{1}{2}\int_{ \Omega} \rho \dot{\mathbf{q}}^T \mathbf{J}^T\mathbf{Y(X)}^T\mathbf{Y(X)}\ d\Omega \\
%   & = \frac{1}{2} \dot{\mathbf{q}}^T \mathbf{J}^T \left[ \int_{ \Omega} \rho \mathbf{Y(X)}^T\mathbf{Y(X)} d\Omega \right] \mathbf{J}\dot{\mathbf{q}} \\
%   & = \frac{1}{2} \dot{\mathbf{q}}^T \mathbf{M} \dot{\mathbf{q}}
% \end{split}
% \text{.}
% \end{equation}
% The second line is a result of the fact that all terms except for $\mathbf{Y(X)}$ are spatially constant, allowing us to move these outside the volume integral, which enables fast assembly of the mass matrix, $\mathbf{M}$.

\subsection{Deformation Gradient}
The deformation at a point $\refX$ in the reference space is given by
\begin{equation}
    \frac{\partial\defX}{\partial \refX} = \sum_{i=1}^m\left(\bld_i\frac{\partial \Pmatxi}{\partial X}\Pi_i\vc{q}_i + \frac{\partial \bld_i}{\partial X}\Pmatxi\Pi_i\vc{q}\right), 
\end{equation}

For physics-based animation, we find that it is sufficient to assume the blending weights are constant in the region around quadrature points, allowing us to discard the second term.
% \dave{gotta deal with this weight gradient}
% At this point we have shown how to fit a polynomial describing the deformation of each surface. With these polynomial coefficients coupled with their associated centers of mass, we can construct an estimate of some arbitrary material point $\mathbf{X}$ using the deformation described by the surface. This lends itself to a general definition for the deformed position of a point as a weighted sum of the polynomials, which yields a unique polynomial for the point. Thus we arrive at a definition for the deformed position, $\mathbf{x}$, of a material point $\mathbf{X}$ in the undeformed space:
% \begin{equation}
% \label{eqn:deformation_map}
% 	\mathbf{x}(\mathbf{X}) = \sum_i^n w_i(\mathbf{X}) \left[ \mathbf{M}(\mathbf{X-\bar{X}}_j)\mathbf{c}_i + \mathbf{t}_j \right]
% 	\text{,}
% \end{equation}
% where we have $n$ surfaces, and $w_i$ and $\mathbf{c}_i$ are the weights and the coefficients for the $i$-th surface, respectively. The terms $\mathbf{\bar{X}}_j$ and $\mathbf{t}_j$ the undeformed and deformed centers of mass, respectively, that are associated with the $i$-th surface.
